### 2023-01-10 paper-thesis/chapters/21-adding-inference.tex
Work on thesis + evcs paper

First, we introduce a new constructor \verb|Infer : Expr -> Expr|, which denotes the variables which could be free. The constructor is introduced when we encounter a \verb|_| variable, a marker that something needs to be inferred.

\begin{lstlisting}
typeOfExpr(s, Var(Syn("_"))) = (Infer(q), qt) :-
	(_, qt) == typeOfExpr(sEmpty(), q).
\end{lstlisting}

Note that the type of \verb|typeOfExpr| has changed, it is now

\begin{lstlisting}
typeOfExpr : scope * Expr -> Expr * Expr
\end{lstlisting}

>>>>

First, we introduce a new constructor \verb|Infer : Expr -> Expr|, which denotes the variables which could be free. The constructor is introduced when we encounter a \verb|_| variable, a marker that something needs to be inferred.
\begin{lstlisting}
typeOfExpr(s, Var(Syn("_"))) = (Infer(q), qt) :-
	(_, qt) == typeOfExpr(sEmpty(), q).
\end{lstlisting}

Note that the type of \verb|typeOfExpr| has changed, it now returns two expressions, the first being the same expression that was passed in except with \verb|_| variables replaced with \verb|Infer| constructors, and the second being the type.
\begin{lstlisting}
typeOfExpr : scope * Expr -> Expr * Expr
\end{lstlisting}
